\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Matplotlib Graphics}
\centerline{Revised: \today}

\section*{Materials}

\begin{itemize}
\item  Today's handouts:  this outline, book chapter, code practice answers, stickers (as needed)
\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers)
\end{itemize}

\section*{Preliminaries}

\begin{itemize}
\item Tools and buzzwords
\begin{itemize}
\item IPython notebooks in Jupyter
\item Graphing with Matplotlib: dataframe plot methods, figure and axis objects
\end{itemize}

\item What is this?
\begin{itemize}
\item Package
\item Pandas
\item {\tt import} statement
\item csv file
\item A dataframe {\tt df}
\item {\tt df.shape}
\item {\tt df.columns}
\item {\tt df.index}
\item Dataframe methods:  \verb|set_index|, {\tt rename}, {\tt drop}
\item The ``x'' and ``y'' variables in the {\tt plot} method
\item Jupyter
\end{itemize}

\item {\bf Exercise}
\begin{itemize}
\item Put red sticker on your laptop

\item Download IPython notebook

%{\small
\url{https://github.com/DaveBackus/Data_Bootcamp/blob/master/Code/IPython/bootcamp_graphics.ipynb}
%}

and save Raw file in your \verb|Data_Bootcamp| directory

In short:  GitHub $\Rightarrow$ Code $\Rightarrow$ IPython $\Rightarrow$ \verb|bootcamp_graphics.ipynb|
$\Rightarrow$ Raw

\item Start Jupyter and open notebook
\item Run this code:
\begin{verbatim}
import pandas as pd
print('Pandas version: ', pd.__version__)
\end{verbatim}
\item Replace red sticker with green when you're set
\end{itemize}

\needspace{3\baselineskip}
\item {\bf Known issues}
\begin{itemize}
\item Notebook has {\tt .txt} extension.  Solution:  In Jupyter, navigate to the file,
click on the box next to it, click on rename at the top, and delete the extension
{\tt .txt}.
\item Windows 10 + Chrome sometimes has no right-click Save As option.
Solution:  Use a different browser.
\item Some Macs generate the error:  {\tt ValueError: unknown locale: UTF-8.}
Solution:  Ask for help. More at StackOverflow:
\url{http://stackoverflow.com/a/19961403/804513}

\begin{comment}
Or maybe:   
import sys
reload sys
sys.setdefaultencoding('utf-8') 
https://youtu.be/5JnMutdy6Fw?t=43m23s
\end{comment} 

\end{itemize}
\end{itemize}


\section*{Python graphics:  Introduction to Matplotlib}

We'll follow the notebook:
\begin{itemize}
\item Jupyter
\item Markdown
\item Preliminaries:  import statements, dataframes to work with
\item Graphing in Excel
\item Apply plot methods to dataframes
\item {\tt plot(x,y)} (skip)
\item Figure and axis objects
\item Recap
\item Bells and whistles
\item Examples
\item Review
\begin{itemize}
\item Put red sticker on, replace with green when done
\end{itemize}
\end{itemize}


\begin{comment}
\section*{Examples}

If time permits, we'll go through some examples of economic and financial data
and its properties.  It's an IPython notebook that you can view on the GitHub repo:
the \verb|Code/IPython| directory,
file \verb|bootcamp_examples.ipynb|.
\end{comment}

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
\item Nothing
\end{itemize}
\item Recommended
\begin{itemize}
\item {\bf Write}:  After class, write down everything you remember without using your notes
\item {\bf Review:} Reread the chapter and fill in anything you missed.
\item Download the {\bf Code Practice A} notebook and work through the questions.
If you have trouble with the download step, keep practicing with notebooks
in the {\tt IPython} and {\tt Lab} directories.
You will need this ability for the exam in a few weeks.
\end{itemize}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

