\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Pandas 1:  Data Input}
\centerline{Revised: \today}


\section*{Materials}

\begin{itemize}
\item  Today's handouts:  this outline, book chapter, code practice, stickers
\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers).
\end{itemize}


\section*{Preliminaries}

\begin{itemize}
\item Tools and buzzwords
\begin{itemize}
\item Packages, import, dataframe, csv files, series, columns, index, API.
\end{itemize}

\item Rules to live by:  don't panic, ask for help

\item What is this?
\begin{itemize}
\item \verb|x = 'abcd'|
\item \verb|x[1]|
\item \verb|'abcd'[1]|
\item \verb|['x1', 'x2']|
\item \verb|d = {'x1': [1, 5, 3], 'x2': [7, 2, 4]}|
\item \verb|d['x1']|
\item \verb|1 > 0|
\item \verb|type(1>0)|
\item Tab completion
\item {\tt object.method?}
\item Function returns
\item Objects and methods
\end{itemize}

\item {\bf Exercise}
\begin{itemize}
\item Put red sticker on your laptop
\item Start Spyder
\item Open blank file \verb|scratch_pad.py| to use in class
\item For second half:  save Python code file in your \verb|Data_Bootcamp| directory: \\
GitHub $\Rightarrow$ Code $\Rightarrow$ Python $\Rightarrow$ \verb|bootcamp_pandas-input.py|
$\Rightarrow$ click on Raw button
\item Raise your hand if you're stuck
\item Replace red sticker with green when you're set
\end{itemize}

\end{itemize}


\section*{Pandas 1: Data input}

We'll follow the book chapter.
\begin{itemize}
\item Packages
\item Importing packages
\item Reading internet files
\item Properties of dataframes
\item Working with variables
\item Dataframe methods
\item Reading files from your computer
\item Examples:  Penn World Table, World Economic Outlook, PISA education data, UN population data and
projections, income by college major
\item APIs:  FRED, World Bank, Fama-French equity returns
\item Review
\begin{itemize}
\item Put red sticker on, replace with green when done
\end{itemize}
\end{itemize}


\section*{Examples}

If time permits, we'll go through some examples of economic and financial data
and its properties.  It's an IPython notebook that you can view on the GitHub repo:
the \verb|Code/IPython| directory,
file \verb|bootcamp_examples.ipynb|.


\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
%\item Review this chapter
\item Code Practice \#3 \\
Submit hardcopy of code file \\
Code template:  GitHub $\Rightarrow$ Code $\Rightarrow$ Python
$\Rightarrow$ \verb|bootcamp_practice_3_template.py|

\end{itemize}
\item Recommended (always)
\begin{itemize}
\item {\bf Write}:  After class, write down everything you remember without using your notes
\item {\bf Review:} Reread the chapter and fill in anything you missed.
\item Ask for help if you get stuck.
\end{itemize}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

