\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Python Fundamentals 1}
\centerline{Revised: \today}


\section*{Materials}

\begin{itemize}
\item  Today's handouts:  this outline, book chapter, code practice, red/green stickers
\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers).
\end{itemize}


\section*{Our approach}

\begin{itemize}
\item Don't panic.
\item Ask for help if you need it.
\item Newbies:  skip things labelled {\it challenging\/} until you're up to it.
\item Apply effort: we call it {\bf bootcamp} for a reason.
\item {\bf Course-work is front-loaded}:  things will slow down in the second half.
\end{itemize}


\section*{Thinking about data}

Not something we'll talk about much in class for a while, but it should be in the back of
your mind over the next 3-4 weeks.  Keep your eyes open for data you want to work with.
Skim the Data sources page of our website.
Ask for help if you find something you can't handle; we're putting together
a collection of programs that read in a variety of datasets, would be happy to add yours
to the list.


\section*{Preliminaries}

\begin{itemize}

\item Tools and buzzwords
\begin{itemize}
\item Google fu, Spyder, syntax, calculations, assignments, strings, lists, built-in functions, methods, tab completion, object inspector
\end{itemize}

\item {\bf Exercise}
\begin{itemize}
\item Put red sticker on your laptop
\item Start Spyder
\item Point out editor and IPython console
\item Open new (empty) file, save as \verb|bootcamp_class_pyfun1.py| in \verb|Data_Bootcamp| directory/folder.  This will serve as your notes for the class.
%\item Raise your hand if you need help
\item Replace red sticker with green when you're set
\end{itemize}


\item Python programs
\begin{itemize}
\item Syntax:  the rules of Python are less flexible than (say) English
\item Not like Excel: they run line by line, like a book
\item Ours will include:  data input, data management, graphics
\item Examples:  Maddison data, OECD healthcare indicators
\end{itemize}
\end{itemize}


\section*{Python fundamentals 1}

We'll follow the book chapter.
\begin{itemize}
\item Calculations %:  \verb| 2*3, 2 * 3, 2/3, 2^3, 2**3 |
\item Assignments
\item The {\tt print()} function
\item Strings
\item Spyder
\item Help
\item Code cells
\item Comments
\item Quotes
\item Lists
\item Tuples
\item Built-in functions:  {\tt len()}, {\tt type()}, conversions
\item Objects and methods, tab completion
\item Python 2 and 3
\item Review
\begin{itemize}
\item Put red sticker on, replace with green when done
\item Exercises marked challenging are optional
\end{itemize}
\end{itemize}

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
%\item Review this chapter
\item Code Practice \#1 due next week (should take about an hour) (we count best 2 of 3)
\end{itemize}
\item Recommended (after every class)
\begin{itemize}
\item {\bf Write}:  Write down everything you remember without using your notes.
\item {\bf Review:} Reread the chapter and fill in anything you missed.
\item Ask for help if you get stuck.
\end{itemize}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

Second half quiz

How do we get Python help in Spyder?
What's the diff between 'Spencer' and "Spencer"?
What does this do?  x = 7, x = x -3.
