\documentclass[11pt]{exam}

\input{../LaTeX/preamble.tex}

%\printanswers

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Code Practice \#1}
\centerline{Revised: \today}

\medskip
{\it Answer each of the questions below.
Include any code you write.
What you hand in can be code or handwritten or something else,
but it must be readable and professional.
Hardcopy only.}

\begin{solution}
Most of these questions answer themselves:  you run the code,
see what happens.  We add short answers for the others.
\end{solution}

\begin{comment}
*** new questions *** 

\item What does this do?  Stat with years as 1987 etc 
\begin{verbatim}
new = int(year/10)*10
\end{verbatim} 
Can you accomplish the same thing by manipulating strings?  

\end{comment} 


\begin{questions}
\item Describe and explain what each of these expressions produces in basic Python:
\begin{verbatim}
2+5
2 + 5
2*5
2/5
2**5
\end{verbatim}

\item What is the value of \texttt{x} after running these statements in order? Why?
\begin{verbatim}
x = 7
x = x + 3
\end{verbatim}

\item What is the value of \texttt{y} after running these statements in order?
Of \texttt{x}?  Why?
\begin{verbatim}
x = 3
y = x
x = 10
\end{verbatim}

\item Does this code run without error?  If so, what does it produce?  If not, explain why.
\begin{verbatim}
x = 3
x = x/2
y = 'abc'
z = y + y
print(x, z)
\end{verbatim}

\item Does this code run without error?  If so, what does it produce?  If not, explain why.
\begin{verbatim}
x = 3
x = x/2
y = 'abc'
z = x + y
print(x, z)
\end{verbatim}

\begin{solution}
We can't add a string ({\tt y = 'abc'}) to a number ({\tt x = 3/2}).
\end{solution}

\needspace{2\baselineskip}
\item Does this code run without error?  If so, what does it produce?  If not, explain why.
\begin{verbatim}
x = 3
y = 24
z = y / x
print(x, y, z, sep=' | ')
\end{verbatim}

\begin{solution}
The {\tt sep} argument controls what comes between things we print.  The default is a single space.
Here we change it to a vertical bar.
If we used \verb|sep=\n|, we would skip to a new line (try it!).
\end{solution}


\item Does this code run without error?  If so, what does it produce?  If not, explain why.
\begin{verbatim}
x = 3
y = '24'
z = y / x
print(x, z)
\end{verbatim}

\item Does this code run without error?  If so, what does it produce?  If not, explain why.
\begin{verbatim}
x = "I am a #string"  # Whoa, a string!
\end{verbatim}

\begin{solution}
The first \verb$#$ is inside a string, so doesn't register in Python as a comment.
\end{solution}

\item Does this code run without error?  If so, what does it produce?  If not, explain why.
\begin{verbatim}
x = [1, 2, 3]
y = [42, 43]
z = x + y
print(z)
\end{verbatim}

\item Does this code run without error?  If so, what does it produce?  If not, explain why.
\begin{verbatim}
x = [1, 2, 3]
y = 42
z = x + y
\end{verbatim}

\begin{solution}
We can't add a number to a list.  The previous example worked because the square brackets in
\verb$[42]$ identify it as a list.
\end{solution}

\item What ``types'' are
\begin{verbatim}
x1 = 12
x2 = 12.0
x3 = '12.0'
x4 = [12]
x5 = [12, 12.0, '12.0']
\end{verbatim}

\item Explain the result of each line:
\begin{verbatim}
type(42)
type(42.0)
type('42.0')
type("42.0")
type("""42.0""")
type([1, 2])
type([1] + [2])
type(1 + 2)
type(print)
\end{verbatim}

\item Describe and explain the result of this statement:
\begin{verbatim}
type(float(str(int('1234'))))
\end{verbatim}

\needspace{2\baselineskip}
\item Describe and explain the result of this statement:
\begin{verbatim}
type(int(float('12.34')))
\end{verbatim}

\begin{solution}
The tricky part of this is the {\tt int}.  When we convert a float to an int,
we eliminate everything after the decimal point.
Thus \verb$int(12.34) = 12$.
\end{solution}

\item Explain each line:
\begin{verbatim}
len([1234])
len("1234")
len(1234)
\end{verbatim}

\begin{solution}
Length is not defined for numbers.  (What would it be?)
\end{solution}

\item What are the type and length of \texttt{x = []}?


% http://tex.stackexchange.com/questions/48632/underscores-in-words-text
\item Convert the string \verb|x = 'abcde'| to a list.  What does it look like?

\item %{\it Challenging.\/}
Consider the integer \texttt{x = 1234}.
\begin{parts}
\item Convert \texttt{x} to a floating point number.
\item Convert \texttt{x} to a string.
\item Convert \texttt{x} to the list
\begin{verbatim}
['1', '2', '3', '4']
\end{verbatim}
\end{parts}

\item {\it Challenging.\/}
How would you convert \texttt{x} to ``title case'' (first letter of each word capitalized)?
{\it Hint:\/} Use tab completion to find an appropriate method.
\begin{verbatim}
x = "luke, i am your father"
\end{verbatim}

\begin{solution}
\verb$x.title()$
\end{solution}

\item {\it Challenging.\/} Consider the string
\begin{verbatim}
x = "How many characters and words are in this string?"
\end{verbatim}
\begin{parts}
\item How many characters does \texttt{x} contain?
\item Convert \texttt{x} to a list of individual characters.
\item Convert \texttt{x} to a list of individual words.
{\it Hint:\/}  Use tab completion to find a method that splits \texttt{x}
into pieces.
\item How many words does \texttt{x} contain?
\end{parts}

\begin{solution}
\begin{verbatim}
a = len(x)
b = list(x)
c = x.split()
d = len(c)
print(a, b, c, d, sep='\n')
\end{verbatim}
\end{solution}

\item Approximately how long did this assignment take you?

\end{questions}

\input{../LaTeX/footer.tex}

\end{document}
